---
title: "Ping Pong"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(ggthemes)
library(scales)
library(plotly)
library(kableExtra)

raw_scores <- read_csv("..//data//scores.csv")

# df for main visual
differences <- raw_scores %>% 
  # Getting the difference number
  mutate(diff = andrew - yuri) %>% 
  # Showing the winner
  mutate(winner = case_when(
    diff > 0 ~ "Andrew",
    TRUE ~ "Yuri"
  )) %>% 
  # Getting scores for the winners. need to make a negative for one of them to match the visual
  mutate(yuri_score = yuri * -1,
         andrew_score = andrew) %>% 
  # Making the actual date a date format
  mutate(date = as.Date(date, tryFormats = c("%m/%d/%Y"))) %>% 
    # Adding a modified_date to include game number
  mutate(modified_date = paste(date, game_number)) 


# The plot for the differences
diff_plot <- differences %>% 
  ggplot(aes(x = modified_date, y = diff, fill = winner)) +
  # fivethirtyeight theme
  theme_fivethirtyeight() +
  # Custom coloring for barchart
  scale_fill_manual("legend", values = c("Andrew" = "#497999", "Yuri" = "#FFA500")) +
  geom_bar(stat = "identity") +
  # Points for andrew
  geom_point(data = differences %>% filter(winner == "Andrew"), aes(x = modified_date, y = andrew_score), color = "#497999") +
  geom_point(data = differences %>% filter(!winner == "Andrew"), aes(x = modified_date, y = andrew_score), color = "#497999", alpha = .15) +
  # points for yuri
  geom_point(data = differences %>% filter(winner == "Yuri"), aes(x = modified_date, y = yuri_score), color = "#FFA500") +
  geom_point(data = differences %>% filter(!winner == "Yuri"), aes(x = modified_date, y = yuri_score), color = "#FFA500", alpha = .15) +
  # adjusting the theme
  theme(
    axis.text.x = element_text(size = 7, angle = 45),
    # reinstituting xlab and ylab because the themefivethirtyeight removes it.
    axis.title = element_text(),
    # removing bg color
    panel.background = element_rect(fill = "white"),
    plot.background = element_rect(fill = "white"),
    legend.background = element_rect(fill = "white")
  ) +
  labs(x = "Date and Game",
       y = "Score Difference") 
  

#### Max Score
max <- differences %>% 
  filter(max_score == 11) %>% 
  select(yuri, andrew, date) %>% 
  rename(Yuri = yuri, 
         Andrew = andrew) %>% 
  gather("key", "value", -date) %>%
  arrange(desc(value)) %>% 
  slice(1)

### Beat
beat <- differences %>% 
  # filter(max_score == 11) %>% 
  select(diff, winner, date, yuri, andrew) %>% 
  mutate(diff = abs(diff)) %>% 
  arrange(desc(diff)) %>% 
  slice(1)

### Streak
streak <- differences %>% 
  dplyr::arrange(game_number) %>% 
  dplyr::arrange(date)
streak <- data.frame(unclass(rle(as.vector(streak$winner)))) %>% 
  arrange(desc(lengths)) %>% 
  slice(1)

```

Row
-----------------------------------------------------------------------

### Game Scores and Differentials

```{r}
plotly::ggplotly(diff_plot, tooltip = c("y"))
```

Column {data-width=350}
-----------------------------------------------------------------------

### Record (All Games)

```{r}
differences %>% 
  select(date, winner) %>%
  group_by(winner) %>% 
  summarise(
    Wins = n()
  ) %>% 
  rename(Player = winner) %>% 
  kable() %>% 
  kable_styling(bootstrap_options  = c("responsive")) %>% 
  row_spec(1, background = "#bcd4e5") %>% 
  row_spec(2, background = "#ffedce") %>% 
  column_spec(1, bold = T)
```

### Record (11-point Games)

```{r}
differences %>% 
  filter(max_score == 11) %>% 
  select(date, winner) %>%
  group_by(winner) %>% 
  summarise(
    Wins = n()
  ) %>% 
  rename(Player = winner) %>% 
  kable() %>% 
  kable_styling(bootstrap_options  = c("responsive")) %>% 
  row_spec(1, background = "#bcd4e5") %>% 
  row_spec(2, background = "#ffedce") %>% 
  column_spec(1, bold = T)
```

### Record (Last 15 Games)

```{r}
differences %>% 
  dplyr::arrange(game_number) %>% 
  dplyr::arrange(date) %>%
  tail(n = 15) %>% 
  select(date, winner) %>%
  group_by(winner) %>% 
  summarise(
    Wins = n()
  ) %>% 
  rename(Player = winner) %>% 
  kable() %>% 
  kable_styling(bootstrap_options  = c("responsive")) %>% 
  row_spec(1, background = "#bcd4e5") %>% 
  row_spec(2, background = "#ffedce") %>% 
  column_spec(1, bold = T)
```

Column {data-width=350}
-----------------------------------------------------------------------
### All Scores
```{r}
differences %>% 
  # arranging to reverse chronological
  dplyr::arrange(desc(game_number)) %>% 
  dplyr::arrange(desc(date)) %>% 
  # only selecting relevant columns
  select(date, winner, andrew, yuri, game_number) %>% 
  # making it pretty
  rename(
    Date = date,
    Winner  = winner,
    `Yuri Score` = yuri,
    `Andrew Score` = andrew,
    `Game Number` = game_number
  ) %>% 
  # For Kableextra, making the winner name the right color
  mutate(Winner = 
    case_when(
      Winner == "Yuri" ~ cell_spec(Winner, background = "#FFA500", color = "white"),
      TRUE ~ cell_spec(Winner, background = "#497999", color = "white")
    )
  ) %>% 
  kable(escape = F) %>% 
  kable_styling("hover")
```

### #FunFacts
**Highest Scored Game (11-pt Games):** `r max$value` points by `r max$key` on `r max$date`
<div style = "height: 10px;"> </div>
**Biggest Beat:** `r beat$winner` won by `r beat$diff` points on `r beat$date` (`r beat$yuri` to `r beat$andrew`)
<div style = "height: 10px;"> </div>
**Longest Streak:** `r streak$values` has the longest winning streak, with a streak of `r streak$lengths` games.
<div style = "height: 10px;"> </div>

**Win Distribution by Game Number:**
```{r}
ggplotly(differences %>% 
           select(winner, game_number) %>% 
           group_by(winner, game_number) %>% 
           summarise(
             Wins = n()
             ) %>%
           ungroup() %>% 
           ggplot(aes(x = game_number, y = Wins, group = winner, fill = winner)) +theme_fivethirtyeight() +
           geom_bar(stat = "identity", position = "dodge") +
           scale_fill_manual("legend", values = c("Andrew" = "#497999", "Yuri" = "#FFA500")) +
         # adjusting the theme
           theme(
             # reinstituting xlab and ylab because the themefivethirtyeight removes it.
             axis.title = element_text(),
             # removing bg color
             panel.background = element_rect(fill = "white"),
             plot.background = element_rect(fill = "white"),
             legend.background = element_rect(fill = "white")
             ),
         height = 300
)

```
